Annotation-Based Empirical Performance Tuning Using Orio

### 2009-02-15 doc/papers/ipdps09/results.tex
git-svn-id: https://svn.mcs.anl.gov/repos/performance/orio@444 e7ad4b5f-b827-0410-872f-f7f4bc3d1efb

The parallel performance results for $T=500$ and $N=4000$ are shown in
Figure~\ref{fig:seidel-cookie-par}. Again we observe that icc failed to
parallelize the code, whereas Pluto was able to parallelize it and Orio
improved the performance of the one-level tiled Pluto code further by up to
128\% (and up to 548\% for the two-level tiled Pluto code). We observed that
tiling over both L1 and L2 can result in worse performance than L1-only
tiling because the number of tiles can be less than the number of cores.
%Similar earlier trend also exists
%in these performance results: Pluto parallelizes the code through its
%polyhedral transformations (i.e., skewing and tiling), while the icc
%compiler alone does not parallelize the loop. Empirical tuning via
%Orio creates up to 122\% speedups over the one-level tiled Pluto code,
%and up to 548\% speedups over the two-level tiled Pluto code. Another
%finding is that tiling for both L1 and L2 caches contributes to a poor
%scalability because the number of tiles can be less than the number of
%processors, resulting in underutilization of the available resources.

@@

The parallel performance results shown in Figure~\ref{fig:lu-cookie-par} were
obtained for $N=4000$. We observe that icc is not able to parallelize the
code, whereas Pluto achieves higher performance by exploiting multicore
parallelism. Furthermore, both Pluto-generated codes have comparable
performance, with slightly better scalability exhibited by the single-level tiled
code. Orio further improved the performance of the Pluto-generated versions
by a factor of 51\% to 120\%.

>>>>

The parallel performance results for $T=500$ and $N=4000$ are shown in
Figure~\ref{fig:seidel-cookie-par}. Again we observe that icc fails to
parallelize the code, whereas Pluto is able to parallelize it and Orio
improves the performance of the one-level tiled Pluto code further by up to
128\% (and up to 548\% for the two-level tiled Pluto code). We observe that
tiling over both L1 and L2 can result in worse performance than L1-only
tiling because the number of tiles can be less than the number of cores.
%Similar earlier trend also exists
%in these performance results: Pluto parallelizes the code through its
%polyhedral transformations (i.e., skewing and tiling), while the icc
%compiler alone does not parallelize the loop. Empirical tuning via
%Orio creates up to 122\% speedups over the one-level tiled Pluto code,
%and up to 548\% speedups over the two-level tiled Pluto code. Another
%finding is that tiling for both L1 and L2 caches contributes to a poor
%scalability because the number of tiles can be less than the number of
%processors, resulting in underutilization of the available resources.

@@

The parallel performance results shown in Figure~\ref{fig:lu-cookie-par} were
obtained for $N=4000$. We observe that icc is not able to parallelize the
code, whereas Pluto achieves higher performance by exploiting multicore
parallelism. Furthermore, both Pluto-generated codes have comparable
performance, with slightly better scalability exhibited by the single-level tiled
code. Orio further improves the performance of the Pluto-generated versions
by a factor of 51\% to 120\%.
